\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-31 standardmodel.tex

We again encourage the reader to read the (pseudo-)Agda-style proof mentioned in our appendix because most of the parts are similar but with more type annotation so it is clearer about the mathematical object doing the interpretation. Here, we need to clarify some ambiguity in our conventional formulation. For example, when we wrote ``$\denotesS{\goodType{\Gamma}{\cC \sigma}{}}$ defined inductively on $\denotesS{\Sigma}$'', the best way to understand is to consider we are defining a function $\denotesS{\goodType{\Gamma}{\cC \_}{}}$ as the interpretation for $\goodType{\Gamma}{\cC \_}{}$ that mapping $\denotesS{\sigma}$ to $\denotesS{\goodType{\Gamma}{\cC \sigma}{}}$ also defined inductively on the length of the signature. The case is similar for $\denotesS{\cL \_}$, $\denotesS{\cCt \_}$ and  $\denotesS{\Sigma \ \_ \ \_}$. \textbf{This is actually the formulation in Agda}---QIIT syntax consider $\cC : "Sig"~\Gamma~n \to "Ty"~\Gamma$ as a constructor and our model needs to interpret this constructor to a function $\cC^S : "Sig"^S \Gamma^S~n \to "Ty"^S~\Gamma^S$ with each judgement also interpreted.

@@

Notice that $\denotesS{\goodSig{\Gamma}{s}{n}}$ and $\denotesS{\goodType{\Gamma}{\cC\sigma}{i}}$ is mutual recursively defined together---because \\ $\goodSealS{\Gamma}{f}{\sigma}{A}$ relies on $\cC$.

>>>>

We encourage the reader to read the (pseudo-)Agda-style proof with more type annotation so it is clearer about the mathematical object doing the interpretation. Here, we need to clarify some ambiguity in our latex formulation. For example, when we wrote ``$\denotesS{\goodType{\Gamma}{\cC \sigma}{}}$ defined inductively on ${\sigma}$'', the best way to understand it is to consider we are defining a function $\denotesS{\goodType{\Gamma}{\cC \_}{}}$ as the interpretation for $\goodType{\Gamma}{\cC \_}{}$ that mapping $\denotesS{\sigma}$ to $\denotesS{\goodType{\Gamma}{\cC \sigma}{}}$, inductively on the length of the signature. The case is similar for $\denotesS{\cL \_}$, $\denotesS{\cCt \_}$ and  $\denotesS{\Sigma \ \_ \ \_}$. \textbf{This is actually the formulation in Agda}---QIIT syntax consider $\cC : "Sig"~\Gamma~n \to "Ty"~\Gamma$ as a constructor and our model needs to interpret this constructor to a function $\cC^S : "Sig"^S \Gamma^S~n \to "Ty"^S~\Gamma^S$ with each judgement also interpreted.

@@

Note that $\denotesS{\goodSig{\Gamma}{s}{n}}$ and $\denotesS{\goodType{\Gamma}{\cC\sigma}{i}}$ is mutual recursively defined together---because \\ $\goodSealS{\Gamma}{f}{\sigma}{A}$ relies on $\cC$.
